% Chapter Template

\chapter{Token Economics} % Main chapter title

\label{Chapter4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Properties and Usage of NVT}

The ERC-20 utility token of the NVT Network (NVT) is a major component of the NVT Network’s decentralized ecosystem. It is designed to be used solely as the primary token of the NVT Network. It is a non-refundable functional utility token that will be used as the unit of exchange between all users of the NVT Network.

NVT will provide a convenient and secure way of payment, reward and settling arrangements between users who explore and interact with the ecosystem of NVT Network. NVT does not in any way represent any shareholding, participation, right, title, or interest in the NVT foundation, its affiliates, or any other company, enterprise or undertaking, nor will NVT entitle token holders to any promise of fees, dividends, revenue, profits, or investment returns and are not indented to constitute securities in Singapore or any relevant jurisdiction.

NVT may only be utilized on the NVT Network and ownership of NVT carries no rights, express or implied other than the right to use NVT as a means to enable usage of and interaction with the NVT Network.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\section{Value Carrier}

NVT can be explained as the virtual crypto fuel of NVT Network, for using certain designed functions, services and tools of the decentralized platform. The economic incentives for users will encourage participants to contribute and take an active role in the decentralized community.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\section{Incentives}
Customer or membership incentive programs bring in new community members and reward existing members for their loyalty. A double-layer incentive mechanism based on the unique PoN (Proof of Network) algorithm is formulated on the platform and used to incentivize the users who contribute positively in the development of the community and ecosystem. In order to be fair to every user of the NVT Network, both creators and explorers will receive NVT as a reward.

Each user can vote for a product or network. There are two major sources of NVT rewards for product creators and explorers. One is user purchased NVT, the other is NVT converted from influence points for completing community and other contribution tasks. Those points are gradually released from the system’s reward pool. There is a limit on the weekly release so everything will be shared according to the pool of users and their performance. The reward pool will shrink every year, allowing for a better adoption rate at early stage. The platform will have a 5 per cent commission fee for the rewards assigned to users, in order to ensure the stability of NVT Network’s economic model.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Reward Setting}

The rewards that each user receives are always calculated accordingly to the order of the time someone sends the data or review during the early stage. The total number of users that participated in a vote, the time, the history and personal score of the user and other variables are taken under consideration during the process.

If a user discovers or predicts that a product will gain in popularity or user preference, the earlier he records his data, the more positive expected returns will receive as a reward for discovering worthy products early.

%----------------------------------------------------------------------------------------

\section{Bonus Malus}

Based on the system being fair, our community will be open and accessible for every user. Users participating will not be limited to those that have no earnings or points. Sharing, participating and being active on the community, will be few ways that someone will be able to get points.

To prevent fake user registration and bot attacks, we do not allow the exchanging of points with NVT Tokens. NVT Token is liquid and can be traded, also there will be limits on maximum points that can be earned. Users can use points for voting and decisions within the community. When points are used in the NVT Community prediction market, they can be converted to NVT Tokens.

%----------------------------------------------------------------------------------------

\section{Surveys and Prediction Market}

Within the NVT community there will be services and tools provided for users to create surveys and prediction requests for particular products, networks or assets. NVT Network will create products which will implement built-in decentralized prediction and assessment protocols.